A comparative analysis of penalized linear mixed models in structured genetic data

### 2020-11-21 main.tex
4.2 figure and interpretation (in progress)

%------------------------------%
\subsection{Motivating example}

@@

%------------------------------%
\subsection{\anna{Lasso and PC-lasso select more population-informative SNPs than LMM-Lasso}}
%------------------------------%

 \begin{figure}[H]
    \centering
    \includegraphics[scale = 0.9]{figures/popInfSNPs_n=200.png}
    \caption{Causal and non-causal SNP selection in the presence of varying levels of population informative SNPs with a coarse 2 Independent Subpopulation structure, dichotomous-discordant effects, $\eta = 0.5$, and $\xi = 0.8$.}
    \label{fig:big_small_gamma}
\end{figure}

>>>>

%------------------------------%
\subsection{Motivating example} \label{sec:example}

@@

%------------------------------%
\subsection{\anna{Lasso and PC-lasso select more population-informative SNPs than LMM-lasso}}
\anna{LMM-lasso is more robust to spurious associations due to allele frequency differences than lasso and PC-lasso }\\
%------------------------------%

As described in Section \ref{sec:example}, differences in allele frequencies have the potential to lead to spurious associations. In the previous section we saw how in the presence of confounding, LMM-lasso and PC-lasso outperform the ordinary lasso in terms of selection accuracy. It is of interest to characterize these methods' selection accuracy in terms of how robust they are to allele frequency differences. To that end, we considered a simplified scenario, with a coarse 2 Independent Subpopulations structure and dichotomous-discordant environmental effects. Figure \ref{fig:pop_inf} shows the relationship between how often a given SNP is selected by the various methods and its absolute difference in  standardized allele frequencies between the two supopulations.

 \begin{figure}[H]
    \centering
    \includegraphics[scale = 0.9]{figures/popInfSNPs_n=200.png}
    \caption{Causal and non-causal SNP selection in the presence of varying levels of population informative SNPs with a coarse 2 Independent Subpopulation structure, dichotomous-discordant effects, $\eta = 0.5$, and $\xi = 0.8$.}
    \label{fig:pop_inf}
\end{figure}

A method which is robust to differences in allele frequencies should show no systematic association between selection proportion and differences in allele frequencies. We see that for both causal and non-causal SNPs, the LMM-lasso and PC-lasso methods exhibit no such association, while the ordinary lasso demonstrates a \anna{substantial} positive trend. \anna{pearson corr with pvalues?}

The presence of this trend for the lasso, and the lack thereof for LMM-lasso and PC-lasso, illustrates the underlying mechanism leading to the superior TPRs of LMM-lasso and PC-lasso compared to that of the lasso in Table \ref{tab:var_sel}.
